% BSP for Bachelor in Game Programming
% english instead of norsk
% oneside for delivery, twoside for book style
\documentclass[BSP,english,oneside]{classes/gucthesis}

% For utf8 encoded .tex files
\usepackage[utf8]{inputenc}

% For colouring text
\usepackage[usenames,dvipsnames]{color}

% For cross references in pdf
\usepackage[pdftex]{graphicx,hyperref}
\hypersetup{
	colorlinks=true,
	linkcolor=Mahogany,
	urlcolor=RoyalBlue
}

% When linking to figures, link to their top, not the text underneat
%\usepackage[hypcap]{caption}	% throws warning..

% Put \capstart after \figure{}[] to get linking right
\usepackage{hypcap}

% For appendix title
\usepackage{appendix}

% For footer on project frontpage
\usepackage{fancyhdr}

% For glossaries
\usepackage[nopostdot]{glossaries}
\usepackage{glossaries-babel}
\input{includes/cogARC_glossaries}
\makenoidxglossaries

% Remove '%' in front of \renewcommand the parent command

% Create command for commenting
\newcommand{\comment}[1]{\textcolor{blue}{\emph{#1}}}
%\renewcommand{\comment}[1]{}

% Create command for todo things
\newcommand{\todo}[1]{{\par\noindent\textbf{\textsc{\color{Gray}todo:}}\color{green}#1}}

% Norwegian Characters,  needs the {} or to be separate from the next letters
% \o{}   \aa{}   \ae{}   so at the end of a word you can use \o  \aa   \ae
% \O{}   \AA{}   \AE{}   you can also just leave a space and latex will remove it
%                        eg,  H\o gskolen i Gj\o vik

% \inlineHeader gives a header that does not show up in the table of content
\newcommand{\inlineHeader}[1]{\addvspace{1.5em}\noindent\makebox[\textwidth][l]{\large\bfseries #1}}


\begin{document}

\input{includes/cogARC_data}

% Create frontpages according to the school template
\makefrontpages

% Create project specific frontpage
\input{includes/cogarc_frontpage}

% Start counting pages after frontpage
\clearpage
\setcounter{page}{1}



% Preface (the * means do not give the chapter a number)
\chapter*{Preface}
	\label{chap:preface}
	\input{includes/cogARC_preface}


\tableofcontents
\listoffigures
\listoftables


% Start with content and count from 1.
\newpage
\setcounter{page}{1}
\pagenumbering{arabic}
% Put introduction here
\part{Introduction}
	
	%\chapter{Introduction}
		\setcounter{page}{2}	% Needed to get numbering right
		\label{chap:introduction}
		\input{includes/cogARC_introduction}

	\chapter{Description and goals}
		\label{chap:description_goals}
		\input{includes/cogARC_description_and_goals}

	% \chapter{Objectives}
		\label{chap:objectives}
		\input{includes/cogARC_objectives}

	\chapter{History and Background}
		\label{chap:background}
		\input{includes/cogARC_history_and_background}

	\chapter{Related work}
		\label{chap:related_work}
		\input{includes/cogARC_related_work}


\part{Design process}

	\chapter{Approach}

	\chapter{Specification}
		\label{chap:specification}
		\input{includes/cogARC_specification}

	\chapter{Game descriptions}
		\label{chap:game_descriptions}
		\input{includes/cogARC_game_descriptions}

	\chapter{Usability}
		\label{chap:usability}
		\input{includes/cogARC_usability}


\part{Development process}

	\chapter{Theory}

	\chapter{Tools}
		\label{chap:tools}

		\section{Unity}
			\input{includes/cogARC_unity}

		\section{Vuforia}
			\input{includes/cogARC_vuforia}

		\section{MonoDevelop}
			\input{includes/cogARC_MonoDevelop}

		\section{GIT}
			\input{includes/cogARC_version_control}

		\section{LaTeX (\LaTeX)}
			\input{includes/cogARC_LaTeX}


	\chapter{Schedule}
		\input{includes/cogARC_schedule}

	\chapter{Process}
		\input{includes/cogARC_development_process}

	\chapter{UnityScript}
		\label{chap:UnityScript}
		\input{includes/cogARC_unityscript}

	\chapter{Unity Serialization}
		\label{chap:UnitySerialization}
		\input{includes/cogARC_unity_serialization}

	\chapter{Program structure}
		\todo{Charts of how objects are connected.}
		\todo{Represent parts of the class diagram to do point 3.3 in the 
		product evaluation good.}

	\chapter{Development changes and decisions}
		\label{chap:Developmentchangesanddecisions}
		\input{includes/cogARC_development_changes}

	\chapter{Program data}
		\todo{Write about the process we had for adding data. How Jakob 
		implemented it at a late point when we were told that this was a 
		"must do".}


\part{Product}

	\chapter{Visual}
		\todo{Put a printscreen of program here}

		\section{Program flow chart}
			\todo{Put a chart here on the flow of the program.}

	\chapter{Application data}
		\todo{Which data are stored in the app and which data is sent to the
				network? This should be a summary of what we have written under
				development.}

	\chapter{Feedback}
		\input{includes/cogARC_feedback}

	\chapter{Future Development}



\part{Summary}

	\chapter{Conclution}
		\input{includes/cogARC_conclution}

	\chapter{Afterword}
		\label{chap:afterword}
		\input{includes/cogARC_afterword}


\todo{Remove this when people know how to use glossaries or before delivery}
Here is an example on how to use glossaries. We can for example use the word
\gls{ECMAScript}. Now we get the text ECMAScript with a link to the glossary
list. In the glossary list there will also be a link to where this is 
referenced in the document. The same applies for \gls{serialization}.

Example of references inside the document:
	Here is a reference to chapter \ref{chap:related_work}.



\part{Appendices}

\appendix %after this line all chapters will have leters instead of numbers
%\appendixpage
%\addappheadtotoc

% References
\bibliographystyle{classes/gucthesis}
\bibliography{includes/cogARC_bibliography}

% Glossary list
\printnoidxglossary[sort=word]

\chapter{Time management}
	\todo{Put the data from Toggl here}




% Examples
% \input{includes/example_packages}

% \input{includes/example_structure}

% \input{includes/example_meetings}

% \GUC, 
% \comment{so what}

% \todo{task \#1}
% This is a todo-task we need to get done.


\end{document}