\paragraph{PlayerPrefsX}
PlayerPrefsX (also known as ArrayPrefs 2)\cite{PlayerPrefsX} is a library created by the Unity community to enhance the built in Player Preference class of Unity.

PlayerPrefsX expands Unitys' way of storing player preferences or other data that the programmer want to persist between sessions.
Unity without PlayerPrefsX supports saving and getting float values, int values and strings. Altough this is all that is needed in most cases, it is sometimes practical to be able to store a bit more complex data.

PlayerPrefsX is able to store vectors, quaternions, arrays and more. 
We used this library to store the list of high scores for each game. 
By using PlayerPrefsX IntArray storing it was very easy to store a array of ten high scores for each game instead of having to either make a complex string to store it or fining another way of storing the scores.

\paragraph{Boomlagoon.{JSON}}
Due to some problems we encountered with the \nameref{sec:UnitySerialization},
we needed to be able to save and restore a structure in another way than the
default one. We spent weeks trying to solve this problem. When we stopped
looking for better ways to solve it, we had ended up on converting the 
structure to {JSON} and save the whole thing as a string.
Unity has some support for {JSON} with it's library called Simple{JSON} 
\cite{SimpleJSON}. Simple{JSON} have the drawback that it only stores data
as a string, which will make the restoration difficult. Instead we found
another implementation of JSON that handles different types.

Boomlagoon.{JSON} is have two main types that we have used. That is 
{JSONO}bject and {JSONV}alue.

\todo{PK: Finish this..}