cogARC is a bachelor project under Gj\o vik University College. We have been
working with \gls{Augmented Reality} to create a tool for cognitive research.
The tool has form as a game with logging functionality that can be used by
researchers. cogARC can typically be used by patients that has suffered stroke
or people with declining cognitive functionality. Doctors, medical staff and/or
researchers can use logging information to get an overview over the cognitiv
situation for the patient and can be enabled to track improvements or
deterioration.

\cite{GenVirtual}

\chapter{Development Team}
The development team consisted of Jakob Sand Svarstad, Per Kristian Warvik and Daniel Granerud.
All of them were taking the bachelor game programming course at Gj\o vik University College for the last three tears from the autumn of 2011. One of the members had never seen a line of code before attending Gj\o vik University College while the two others had some experience with coding.

Two of the team members have worked together continuously troughout the  troughout the their time at Gj\o vik University College, but as a team we have only worked together on one project. We found out that we worked well together on that project and decided that we would work well together on a bigger project as well.

\chapter{Externals}

\section{Employer}

\section{Supervisor}
Our supervisor for this project has been Simon McCallum.

% \chapter{Project Description}

% \section{Reasons for creating this thing}

% \section{Implementation plan}
% %How we planned to implement this

% \section{Group Organization}
% %How we as a group organized ourself and the work

% \section{Report Organization}
% %How the report is organized, what each chapter is and short about structural layout.

% \section{Project Goals}
% %Our goals in this project, how far we want the project to go and how complete we hope it will be. What parts will be implemented and such



% What is the setting of the problem? This is, in other words, the background. In some cases, this may be implicit, and in some cases, merged with the motivation below.
% What exactly is the problem you are trying to solve? This is the problem statement.
% Why is the problem important to solve? This is the motivation. In some cases, it may be implicit in the background, or the problem statement itself.
% Is the problem still unsolved? The constitutes the statement of past/related work crisply.
% Why is the problem difficult to solve? This is the statement of challenges. In some cases, it may be implicit in the problem statement. In others, you may have to say explicitly as to why the problem is worthy of a BTech/MTech/PhD, or a semester project, as the case may be.
% How have you solved the problem? Here you state the essence of your approach. This is of course expanded upon later, but it must be stated explicitly here.
% What are the conditions under which your solution is applicable? This is a statement of assumptions.
% What are the main results? You have to present the main summary of the results here.
% What is the summary of your contributions? This in some cases may be implicit in the rest of the introduction. Sometimes it helps to state contributions explicitly.
% How is the rest of the report organized? Here you include a paragraph on the flow of ideas in the rest of the report. For any report beyond 4-5 pages, this is a must.