All requirements for this project was created based on a design document given to us by our employer.
As we were not given any concrete requirements outside of the design of the individual minigames we
were left to create them based on this.


\subsection{Operational requirements}
Based on the design document we were able to create a small set of goals that had to be reached for this project
to be considered complete and operational by us.
Based on the design document we created the goals of creating a set of minigames that:
%The goals of this project is to create a set of mini-games that:
\begin{itemize}
	\item Tests the players' cognitivity and to slow down their cognitive decline.
	\item Keeps track of the players' cognitive performance.
	\item Track and document the cognitive changes.
	\item Uses AR to provide a new experience.
\end{itemize}

\subsection{Functional requirements}
When considering functional requirements we found that there were some requirements that would have to be there to make the program do what the design document specified. 
The markers on the cubes would have to be seen. 
In our case we have used the library \gls{Vuforia} to handle all input from the camera.
This means that we had no influence on the direct observation on the cubes. 
Vuforia would analyze images from the camera and give us positions of the different trackers when they were observed. 
In our situation, the chance we had to influence here lies in how we handle the input we get. 
We have written more about this opportunity in chapter \ref{sec:AR_library_integration} \nameref{sec:AR_library_integration}.

\paragraph{Logging}
Our employer originally wanted us to log the hand movements of the user when the user is playing the game. 
With the META SpaceGlasses this is supposedly possible, but as of the writing of this report the SDK for the SpaceGlasses have yet to ship. 
In the beginning of the project we looked into doing this with the technology we were going to use for the project, Unity and Vuforia. 
We looked into this, but found that neither Unity or Vuforia support any kind of tracking of hands. 
We brought this issue to our employer and after telling him of our findings we were told that we could then drop logging of the players hand movements altogether. 
He said he also wanted logging of certain other events, but we could save this for last and do it if we had time to implement it.

%\subsection{Usability requirements}
%\todo{write}
